Glyph-maps for visualizing climate data and models

### 2011-08-31 paper.tex
massaged math

\begin{eqnarray*}\label{coords.eqn}
x_\text{ coordinate}&=& x_{\amaj} + w \cdot x_{\amin}\\
y_\text{ coordinate}&=& y_{\amaj} + h \cdot y_{\amin}
\end{eqnarray*}
where $w$ and $h$ are width and height respectively. The width and height will typically take into account the resolution of the major and minor axes, that is the minimum difference between consecutive locations.

Computing the coordinates for star glyphs is achieved by using polar coordinates,  $r=y_{\amin}$, and $\theta=x_{\amin}$, both scaled to be between 0 and 1. Then the glyph coordinates are given by

\begin{eqnarray*}\label{coords.polar.eqn}
x_\text{ coordinate}&=& x_{\amaj} + \frac{w \cdot r}{2} \sin(2 \pi \theta)\\
y_\text{ coordinate}&=& y_{\amaj} + \frac{h \cdot r}{2} \cos(2 \pi \theta)
\end{eqnarray*}

>>>>

\begin{equation}
\begin{array}{lll}
x_\text{ coordinate}&=& x_{\amaj} + w \cdot x_{\amin}\\
y_\text{ coordinate}&=& y_{\amaj} + h \cdot y_{\amin}, 
\end{array}\label{coords.eqn}
\end{equation}
where $w$ and $h$ are width and height respectively. The width and height will typically take into account the resolution of the major and minor axes, that is the minimum difference between consecutive locations.

Computing the coordinates for star glyphs is achieved by using polar coordinates,  $r=y_{\amin}$, and $\theta=x_{\amin}$, both scaled to be between 0 and 1. Then the glyph coordinates are given by 
\begin{equation}
\begin{array}{lll}
x_\text{ coordinate}&=& x_{\amaj} + \frac{w \cdot r}{2} \sin(2 \pi \theta) \\
y_\text{ coordinate}&=& y_{\amaj} + \frac{h \cdot r}{2} \cos(2 \pi \theta).
\end{array}\label{coords.polar.eqn}
\end{equation}
Note that this is is a non-standard conversion to polar coordinates, but this conversion provides us with a time line that starts at 12 o'clock and wraps around the origin in a clockwise fashion.
